---
title: "displayERUM"
author: "dan carver"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(raster)
library(tmap)
library(sf)
tmap_mode("plot")

saveMap <- function(map, name){
  tmap_save(tm = map, filename = paste0("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/", name,".png"),
            width = 12, height = 15, units = "in", dpi = 600)
}
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
### read in some addational information for the 
ecos <- sf::st_read("F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/Omeric_ecoregionsOfInterest.shp")
states <- sf::st_read("F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/statesOfInterest.shp")
grad <- sf::st_read("F:/nrelD/genericSpatialData/world/ne_10m_graticules_all/ne_10m_graticules_5.shp")
grad1 <- grad
proj <- raster::crs("+proj=lcc +lon_0=-95 +lat_1=49 +lat_2=77")
grad <- sf::st_transform(grad, crs(proj)) %>%
  sf::st_crop(states)

### read in point data 
d1 <- read.csv("F:/nrelD/usda/rcJohnson/analysisData/ERUMlocationMeansv621Climate 19dec19.csv")
d1$Latitude.1 <- as.numeric(d1$Latitude.1)
d1$Longitude.1 <- as.numeric(d1$Longitude.1)
p1 <- st_as_sf(x = d1, coords = c("Longitude.1","Latitude.1"), crs = crs(grad1))
p1 <- sf::st_transform(p1, crs(proj))
```



## Visaulize the projections 

### Can 1
```{r echo = FALSE, message = FALSE, warning = FALSE }
# Read in Raster 
# Set values outside the min max range to NA 
# use the information below to set categories in tmap 
r1 <- raster::raster("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/Can1_Oeco.tif")
r1[r1[] < -2.2464,] <- NA
r1[r1[] > 1.7391, ] <- NA

b1 <- c(-1.9807, -1.7150, -1.4493, -1.1836,-0.9179, -0.6522, -0.3865, -0.1208, 0.1449, 0.4106, 0.676,0.9420 ,1.2077,1.4734,1.7391)
map <- tm_shape(shp = r1) + 
  tm_raster(  style = "fixed",
              breaks = b1,
              palette = "-Spectral")+
  tm_layout(legend.outside = TRUE) 
saveMap(map = map, name = "Can1_Oeco")

```

```{r}
###genating final maps 
## add states and ecoregions 
m2 <- tm_shape(states) + 
    tm_polygons(col = "white", border.col = "black") +
  tm_shape(grad) + 
  tm_lines(lty = "dashed", col = "black")+ 
  tm_shape(ecos)+ 
    tm_polygons(col = "white", border.col = "white") + 
  map +
    tm_shape(ecos)+ 
  tm_borders(col = "black") 

m3 <- m2 + tm_scale_bar(color.dark = "gray60",
    position = c("left", "bottom")) +
  tm_shape(p1) +
    tm_dots(size = 0.2, col = "black")

tmap_save(tm = m3, filename = "F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/mapsFromR/can1_OEcoData.jpeg", dpi = 600, )

```
<br>
map with contours 

Canonical variate 1

Can 1=-9.79818 + mat (0.3032) + TD (0.25038) + map (0.00327) + msp (-0.00337) + ahm (-0.01356) + PAS (-0.00264) + emt (-0.05372)

R2= 0.85

Can 1	
	Observed data mapping intervals at .01 CI
- 1	-2.2464	-1.9807

- 2	-1.9807	-1.7150

- 3	-1.7150	-1.4493

- 4	-1.4493	-1.1836

- 5	-1.1836	-0.9179

- 6	-0.9179	-0.6522

- 7	-0.6522	-0.3865

- 8	-0.3865	-0.1208

- 9	-0.1208	0.1449

- 10	0.1449	0.4106

- 11	0.4106	0.6763

- 12	0.6763	0.9420

- 13	0.9420	1.2077

- 14	1.2077	1.4734

- 15	1.4734	1.7391



### Can 2
```{r }
# Read in Raster 
# Set values outside the min max range to NA 
# use the information below to set categories in tmap 
r1 <- raster::raster("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/Can2_Oeco.tif")
r1[r1[] < -3.1078,] <- NA
r1[r1[] > 1.3997, ] <- NA

b1 <- c(-2.8073,-2.5068,-2.2063,-1.9058,-1.6053,-1.3048,-1.0043,-0.7038,-0.4033,-0.1028,0.1977,0.4982,0.7987,1.0992,1.3997)
r2 <- raster::rasterToContour(x = r1, nlevels = length(b1), levels = b1)


map <- tm_shape(shp = r1) + 
  tm_raster(  style = "fixed",
              breaks = b1,
              palette = "-Spectral")+
  tm_layout(legend.outside = TRUE) 

```

```{r}
###genating final maps 
## add states and ecoregions 
m2 <-   tm_shape(states) + 
    tm_polygons(col = "white", border.col = "black") +
  tm_shape(grad) + 
  tm_lines(lty = "dashed", col = "black")+ 
  tm_shape(ecos)+ 
    tm_polygons(col = "white", border.col = "white") + 
  map +
    tm_shape(ecos)+ 
  tm_borders(col = "black") 

m3 <- m2 + tm_scale_bar(color.dark = "gray60",
    position = c("left", "bottom")) +
  tm_shape(p1) +
    tm_dots(size = 0.2, col = "black")

tmap_save(tm = m3, filename = "F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/mapsFromR/can2_OEcoData.jpeg", dpi = 600, )

```
<br>
Map with contours

Canonical variate 2

Can 2 = -25.8418 + mat (-1.7214) + mcmt (0.50829) + map (0.00156) + ahm (0.02009) + nffd (0.05013) + emt (-0.11856) + ext (0.65382)

R2 = 0.81

Can2		
	Observed data mapping intervals at .01 CI
- 1	-3.1078	-2.8073

- 2	-2.8073	-2.5068

- 3	-2.5068	-2.2063

- 4	-2.2063	-1.9058

- 5	-1.9058	-1.6053

- 6	-1.6053	-1.3048

- 7	-1.3048	-1.0043

- 8	-1.0043	-0.7038

- 9	-0.7038	-0.4033

- 10 -0.4033	-0.1028

- 11	-0.1028	0.1977

- 12	0.1977	0.4982

- 13	0.4982	0.7987

- 14	0.7987	1.0992

- 15	1.0992	1.3997





### Shoot Weight 
```{r }
# Read in Raster 
# Set values outside the min max range to NA 
# use the information below to set categories in tmap 
r1 <- raster::raster("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/Shootwt_Oeco.tif")
r1[r1[] < 0,] <- NA
r1[r1[] > 354.6, ] <- NA


b1 <- c(39.4,78.8,118.2,157.6,197,236.4,275.8,315.2,354.6)
r2 <- raster::rasterToContour(x = r1, nlevels = length(b1), levels = b1)

map <- tm_shape(shp = r1) + 
  tm_raster(  style = "fixed",
              breaks = b1,
              palette = "-Spectral")+
  tm_layout(legend.outside = TRUE) 
#saveMap(map = map, name = "bloomDay")

```

```{r}
###genating final maps 
## add states and ecoregions 
m2 <-   tm_shape(states) + 
    tm_polygons(col = "white", border.col = "black") +
  tm_shape(grad) + 
  tm_lines(lty = "dashed", col = "black")+ 
  tm_shape(ecos)+ 
    tm_polygons(col = "white", border.col = "white") + 
  map +
    tm_shape(ecos)+ 
  tm_borders(col = "black") 

m3 <- m2 + tm_scale_bar(color.dark = "gray60",
    position = c("left", "bottom")) +
  tm_shape(p1) +
    tm_dots(size = 0.2, col = "black")

tmap_save(tm = m3, filename = "F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/mapsFromR/shootWeight_OEcoData.jpeg", dpi = 600, )

```
<br>
Map with Countours

Shoot wt.

Shoot wt. = -69.2096 + mat (38.72942) + mcmt (-46.7416) + map (0.31101) + pas (-0.37035) + emt (10.9494)

R2 = 0.59

Shoot wt.	
	Observed data mapping intervals at .01 CI
	
- 1	0	39.4

- 2	39.4	78.8

- 3	78.8	118.2

- 4	118.2	157.6

- 5	157.6	197

- 6	197	236.4

- 7	236.4	275.8

- 8	275.8	315.2

- 9	315.2	354.6



### Bloom Day

```{r }
# Read in Raster 
# Set values outside the min max range to NA 
# use the information below to set categories in tmap 
r1 <- raster::raster("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/Bloomday_Oeco.tif")
### state boundary 
# r1 <- raster::raster("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/Bloomday.tif")
r1[r1[] < 136.5,] <- NA
r1[r1[] > 182.1, ] <- NA



b1 <-c(142.2,147.9,153.6,159.3,165,170.7,176.4,182.1)
r2 <- raster::rasterToContour(x = r1, nlevels = length(b1), levels = b1)


map <- tm_shape(shp = r1) + 
  tm_raster(  style = "fixed",
              breaks = b1,
              palette = "-Spectral")+
  tm_layout(legend.outside = TRUE) 
#saveMap(map = map, name = "bloomDay")

```

```{r}
###genating final maps 
## add states and ecoregions 
m2 <-   tm_shape(states) + 
    tm_polygons(col = "white", border.col = "black") +
  tm_shape(grad) + 
  tm_lines(lty = "dashed", col = "black")+ 
  tm_shape(ecos)+ 
    tm_polygons(col = "white", border.col = "white") + 
  map +
    tm_shape(ecos)+ 
  tm_borders(col = "black") 

m3 <- m2 + tm_scale_bar(color.dark = "gray60",
    position = c("left", "bottom")) +
  tm_shape(p1) +
    tm_dots(size = 0.2, col = "black")

tmap_save(tm = m3, filename = "F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/mapsFromR/bloomDay_OEcoData.jpeg", dpi = 600, )

```

<br>
Map without  contours
```{r echo = FALSE, message = FALSE, warning = FALSE }

map <- map + tm_shape(shp = r2) +
  tm_lines(col = "white", lwd = 0.2 )
map
saveMap(map = map, name = "BloomDayContour")

```
<br>
map with contours

Bloom day

Bloom day = 400.9691 + mat (28.63729) + mcmt (-14.2239) + ahm (-0.37372) + nffd (-0.48261) + emt (2.59468) + ext (-7.94837) 

R2 = 0.75

Bloom day	
	Observed data mapping intervals at .01 CI
	
- 1	136.5	142.2

- 2	142.2	147.9

- 3	147.9	153.6

- 4	153.6	159.3

- 5	159.3	165

- 6	165	170.7

- 7	170.7	176.4

- 8	176.4	182.1



### Umbel Width 
```{r }
# Read in Raster 
# Set values outside the min max range to NA 
# use the information below to set categories in tmap 
r1 <- raster::raster("F:/nrelD/usda/rcJohnson/buckwheat/projectedOutputs/Umbelwidth_Oeco.tif")
r1[r1[] < 2.6,] <- NA
r1[r1[] > 23.02, ] <- NA
#tmap_mode("view")


b1 <-c(4.32,6.02,7.72,9.42,11.12,12.82,14.52,16.22,17.92,19.62,21.32,23.02)
r2 <- raster::rasterToContour(x = r1, nlevels = length(b1), levels = b1)


map <- tm_shape(shp = r1) + 
  tm_raster(  style = "fixed",
              breaks = b1,
              palette = "-Spectral")+
  tm_layout(legend.outside = TRUE) 

```

```{r}
###genating final maps 
## add states and ecoregions 
m2 <-   tm_shape(states) + 
    tm_polygons(col = "white", border.col = "black") +
  tm_shape(grad) + 
  tm_lines(lty = "dashed", col = "black")+ 
  tm_shape(ecos)+ 
    tm_polygons(col = "white", border.col = "white") + 
  map +
    tm_shape(ecos)+ 
  tm_borders(col = "black") 

m3 <- m2 + tm_scale_bar(color.dark = "gray60",
    position = c("left", "bottom")) +
  tm_shape(p1) +
    tm_dots(size = 0.2, col = "black")

tmap_save(tm = m3, filename = "F:/nrelD/usda/rcJohnson/buckwheat/finalMaps/mapsFromR/umbelWidth_OEcoData.jpeg", dpi = 600, )

```
<br>
Map with contours 

Umbel width

Umbel width = 26.46658 + mat (5.26435) + mwmt (-12.1966) + mcmt (9.09411) + td (11.323) + 
ahm (-0.07219) + ext (-1.09539) 


R2 = 0.62

Umbel width	Observed mapping intervals at .01 CI

- 1	2.6	4.32

- 2	4.3	6.02

- 3	6	7.72

- 4	7.7	9.42

- 5	9.4	11.12

- 6	11.1	12.82

- 7	12.8	14.52

- 8	14.5	16.22

- 9	16.2	17.92

- 10	17.9	19.62

- 11	19.6	21.32

- 12	21.3	23.02



